Solving the maximum independant set problem by generic programming einsum networks

### 2021-06-16 paper/paper.tex
new data

\centerline{\begin{tikzpicture}
    \def\dx{0};
    \def\r{0.25}
    \def\ax{0}
    \def\ay{0}
    \def\bx{1}
    \def\by{1}
    \def\cx{1}
    \def\cy{-1}
    \filldraw[fill=black] (\ax+\dx,\ax) circle [radius=\r];
    \filldraw[fill=black] (\bx+\dx,\by) circle [radius=\r];
    \filldraw[fill=black] (\cx+\dx,\cy) circle [radius=\r];
    \draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx+0.2,0.5*\ay+0.5*\by-0.2) .. (\bx+\dx,\by);
    \draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx-0.2,0.5*\ay+0.5*\by+0.2) .. (\bx+\dx,\by);
    \draw [black,thick] (\ax+\dx,\ay) -- (\cx+\dx,\cy);
    \draw [black,thick] (\ax+\dx,\ay) -- (\ax+\dx-0.6,\ay);
    \draw [black,thick] (\bx+\dx,\by) -- (\bx+\dx+0.6,\by);
    \node[color=white] at (\ax+\dx,\ax) {A};
    \node[color=white] at (\bx+\dx,\by) {B};
    \node[color=white] at (\cx+\dx,\cy) {V};
\end{tikzpicture}}

@@

\subsection{The tensor network compression detects branching rules automatically}
In the following, we are going to show tropical tensor networks with least restrictive principle can automatically discover branching rules.
We denote the effective branching number of contracting the local degrees of freedoms as $|T_S|_{\neq -\infty}/2^{|S|}$, where $|\cdot|_{\neq -\infty}$ is the number of nonzero elements in a tropical tensor.

>>>>

\centerline{\begin{tikzpicture}
    \def\dx{0};
    \def\r{0.25}
    \def\ax{0}
    \def\ay{0}
    \def\bx{1}
    \def\by{1}
    \def\cx{1}
    \def\cy{-1}
    \filldraw[fill=black] (\ax+\dx,\ax) circle [radius=\r];
    \filldraw[fill=black] (\bx+\dx,\by) circle [radius=\r];
    \filldraw[fill=black] (\cx+\dx,\cy) circle [radius=\r];
    %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx+0.2,0.5*\ay+0.5*\by-0.2) .. (\bx+\dx,\by);
    %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx-0.2,0.5*\ay+0.5*\by+0.2) .. (\bx+\dx,\by);
    \draw [black,thick] (\ax+\dx,\ay) -- (\bx+\dx,\by);
    \draw [black,thick] (\ax+\dx,\ay) -- (\cx+\dx,\cy);
    \draw [black,thick] (\ax+\dx,\ay) -- (\ax+\dx-0.8,\ay);
    \draw [black,thick] (\bx+\dx,\by) -- (\bx+\dx+0.8,\by);
    \node[color=white] at (\ax+\dx,\ax) {A};
    \node[color=white] at (\bx+\dx,\by) {B};
    \node[color=black] at (0.5*\ax+0.5*\bx-0.2+\dx,0.5*\ay+0.5\by+0.2) {k};
    \node[color=black] at (0.5*\ax+0.5*\cx+\dx+0.2,0.5*\ay+0.5\cy+0.2) {j};
    \node[color=black] at (\ax+\dx-0.5,\ay-0.2) {i};
    \node[color=black] at (\bx+\dx+0.5,\by-0.2) {l};
    \node[color=white] at (\cx+\dx,\cy) {V};
\end{tikzpicture}}

@@

\subsection{The tensor network compression detects branching rules automatically}
In the following, we are going to show tropical tensor networks with least restrictive principle can automatically discover branching rules.
We denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
It is the effective degree of freedoms per vertex in $R$.
